Increasing Performance via Gamification in a Volunteer-Based Evolutionary Computation System

### 2018-01-09 2018-IPMU/Gamification/paper.tex
Down to 11 pages
Suppressed some paragraphs and citations. Closes #8
Also @mariosky regot figure 1 in a single chart, so closes #10

Gamification techniques in a volunteer context seeks to persuade
users to use their natural desire to compete, learn and socialize in
given non-game context application \cite{deterding2011game,hamari2014does}.
Some works give a form of reward to users, these include
points \cite{sutter2010browse}, achievement badges or levels \cite{hamari2011framework},
the filling of a progress bar \cite{o2010get}, or providing the user with virtual currency.
By Making the rewards for  tasks achievements visible to other players or
providing leader boards are ways of encouraging players to compete \cite{hickman2010total}. In this work, a leader board was implemented in order to promote competition, presenting only the all-time top five participating users. Competition can also have problematic consequences, which can result in
negative conduct, low cooperation and collaboration, or disadvantaging certain player demographics
such as women \cite{kumar2013gamification}.

@@

This work has been supported in part by: Ministerio espa\~{n}ol de
 Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-3-P
 (UGR-EPHEMECH).

>>>>

Gamification techniques in a volunteer context seeks to persuade
users to use their natural desire to compete, learn and socialize in
given non-game context application \cite{deterding2011game,hamari2014does}.
% Some works give a form of reward to users, these include
% points \cite{sutter2010browse}, achievement badges or levels \cite{hamari2011framework},
% the filling of a progress bar \cite{o2010get}, or providing the user with virtual currency.
By Making the rewards for  tasks achievements visible to other players or
providing leader boards are ways of encouraging players to compete
\cite{hickman2010total}. In this work, a leader board was implemented
in order to promote competition, presenting only the all-time top five
participating users.
% Competition can also have problematic consequences, which can result in
% negative conduct, low cooperation and collaboration, or disadvantaging certain player demographics
% such as women \cite{kumar2013gamification}.

@@

This work has been supported in part by: Ministerio espa\~{n}ol de
 Econom\'{\i}a y Competitividad under projects TIN2014-56494-C4-3-P
 (UGR-EPHEMECH) and TIN2017-85727-C4-2-P (UGR-DeepBio).
